---
title: "The Impact of Long-Term O3 Exposure on Specific Causes of Death"
substitle: "Effect Modification in a US Medicare Cohort"
author: "Fatemeh Kazemi"
date: "2/20/2021"
output: html_document
---

### Variables           - description
    1. SiteID           - unique identifier of each monitor (site)
    2. year             - year
    3. month            - month
    4. age              - age
                          a. in all analysis 
                             65, 66, ..., 90
                          b. in Age effect modification analysis
                             LE75 : less than/equal to 75
                             M75 : More than 75
    5. sex              - sex (F/M)
    6. race             - race 
                          a. in all analysis
                              W  : White
                              NW : Nonwhite
                          b. in Race effect modification analysis
                              A  : Asian
                              B  : Black
                              H  : Hispanic
                              N  : Native American
                              W  : White
    7. StrID            - age-sex-race(asr) strata
    8. no_enrollee      - number of Medicare enrollees of each asr group in each
                          location at the beginning of the month 
    9. no_death_cause   - number of death at each asr group for each cause in 
                          month t for each location
   10. O3maxh           - warm season avg of max daily o3 for each calender year
                          at the given site
   11. O3avgh           - warm season avg of daily avg o3 for each calender year
                          at the given site
   12. O3max8h          - warm season avg of 8h-max daily o3 for each calender year
                          at the given site
   13. PM               - PM2.5 yearly average over the previous year at the 
                          given site up to the given month
   14. ses              - xxx
   15. LocationSetting  - location setting
                          a. URBAN AND CENTER CITY
                          b. SUBURBAN
                          c. RURAL
   16. RegionIV     	  - region as defined in the paper:  1, 2, 3, 4 
                          1 : West
                          2 : Midwest
                          3 : South
                          4 : Northeast
   17. State      	    - state of residence
   18. NO2              - NO2 yearly average over the previous year at the 
                          given site up to the given month
   19. sescat           - SES category for urban or urban/suburban areas

### Models
    1. 
    
###
srun -p short --pty --export=ALL -N 1 --mem=200Gb --time=24:00:00 /bin/bash
/shared/centos7/r-project/3.6.1/bin/R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r load packages}
  library(tidyverse)
  library(here)
  library(survival)
```

```{r load data}
load(here('data','analysis','ndi-ozone.RDa'))
load(here('data','analysis','ndi-ozone-no2.RDa'))
load(here('data','analysis','ndi-ozone-age.RDa'))
load(here('data','analysis','ndi-ozone-race.RDa'))
```

```{r }
cuz <- c("allcuz","nacc","acc",
         "cvd","ihd","chf","cbv",
         "resp","copd","pneu","uri","ards",
         "canc","lungc",
         "seps",
         "VaD","AD","NeD","UsD",
         "diabt1", "diabt2", "diab",
         "kidn")

cuz1 <- c("allcuz","nacc","acc",
         "cvd","ihd")

cuz2 <- c("chf","cbv",
         "resp","copd","pneu","uri")

cuz3 <- c("ards",
         "canc","lungc",
         "seps",
         "VaD","AD")

cuz4 <- c("NeD","UsD",
         "diabt1", "diabt2", "diab",
         "kidn")
```

```{r base}
out.base = matrix(nrow = 1, ncol = 3, byrow = T) 
colnames(out.base) <- c("Outcome", "O3_B", "O3_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 3, byrow = T) 
  colnames(out) <- c("Outcome", "O3_B", "O3_SE")
  out[1,1] <- Y
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh', 2]
  out.base <- rbind(out.base, out) 
}
save(out.base, 
     file = here('output', 'analysis', 'out-base-4.RDa'))

```

```{r state}
out.state = matrix(nrow = 1, ncol = 3, byrow = T) 
colnames(out.state) <- c("Outcome", "O3_B", "O3_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + State + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 3, byrow = T) 
  colnames(out) <- c("Outcome", "O3_B", "O3_SE")
  out[1,1] <- Y
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh', 2]
  out.state <- rbind(out.state, out) 
}
save(out.state, 
     file = here('output', 'analysis', 'out-state-4.RDa'))

```

```{r ses}
out.ses = matrix(nrow = 1, ncol = 3, byrow = T) 
colnames(out.ses) <- c("Outcome", "O3_B", "O3_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 3, byrow = T) 
  colnames(out) <- c("Outcome", "O3_B", "O3_SE")
  out[1,1] <- Y
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh', 2]
  out.ses <- rbind(out.ses, out) 
}
save(out.ses, 
     file = here('output', 'analysis', 'out-ses-4.RDa'))

```

```{r pm}
out.pm = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm <- rbind(out.pm, out) 
}

save(out.pm, 
     file = here('output', 'analysis', 'out-pm-4.RDa'))

```

```{r no2}
out.no2 = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.no2) <- c("Outcome","O3_B","O3_SE","NO2_B","NO2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.no2[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + NO2 + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.no2, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","NO2_B","NO2_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh',2]
  # NO2
  out[1,4] <- coef(glm_model)['NO2']
  out[1,5] <- summary(glm_model)$coefficients['NO2',2] 
  out.no2 <- rbind(out.no2, out) 
}
save(out.no2, 
     file = here('output', 'analysis', 'out-no2-4.RDa'))

```

```{r age}
dt.ndi.ozone.age$age<-as.factor(dt.ndi.ozone.age$age)

### Age LE75
dt.ndi.ozone.age$age <- relevel(dt.ndi.ozone.age$age, ref = "LE75") 
age.le = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(age.le) <- c("Age_Cat","Outcome","O3_B","O3_SE","pValue")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.age[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*age + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.age, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Age_Cat","Outcome","O3_B","O3_SE","pValue")
  out[1,1] <- "LE75" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:ageM75',4]
  age.le <- rbind(age.le, out)
}

save(age.le, 
     file = here('output', 'analysis', 'out-le-4.RDa'))

### Age M75
dt.ndi.ozone.age$age <- relevel(dt.ndi.ozone.age$age, ref = "M75") 
age.mt = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(age.mt) <- c("Age_Cat","Outcome","O3_B","O3_SE","pValue")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.age[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*age + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.age, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Age_Cat","Outcome","O3_B","O3_SE","pValue")
  out[1,1] <- "M75" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:ageLE75',4]
  age.mt <- rbind(age.mt, out)
}

save(age.mt, 
     file = here('output', 'analysis', 'out-mt-4.RDa'))

out.age <-na.omit(rbind(age.le, age.mt))
save(out.age, 
     file = here('output', 'analysis', 'out-age.RDa'))

```

```{r sex}
dt.ndi.ozone$sex<-as.factor(dt.ndi.ozone$sex)

### sex Female
dt.ndi.ozone$sex <- relevel(dt.ndi.ozone$sex, ref = "F") 
sex.F = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(sex.F) <- c("sex_Cat","Outcome","O3_B","O3_SE","pValue")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sex + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("sex_Cat","Outcome","O3_B","O3_SE","pValue")
  out[1,1] <- "F" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sexM',4]
  sex.F <- rbind(sex.F, out)
}

save(sex.F, 
     file = here('output', 'analysis', 'out-sexF-4.RDa'))

### sex Male
dt.ndi.ozone$sex <- relevel(dt.ndi.ozone$sex, ref = "M") 
sex.M = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(sex.M) <- c("sex_Cat","Outcome","O3_B","O3_SE","pValue")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sex + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("sex_Cat","Outcome","O3_B","O3_SE","pValue")
  out[1,1] <- "M" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sexF',4]
  sex.M <- rbind(sex.M, out)
}

save(sex.M, 
     file = here('output', 'analysis', 'out-sexM-4.RDa'))

out.sex <-na.omit(rbind(sex.F, sex.M))
save(out.sex, 
     file = here('output', 'analysis', 'out-sex.RDa'))

```

```{r race}
dt.ndi.ozone.race$race <- as.factor(dt.ndi.ozone.race$race)

### race Asian
dt.ndi.ozone.race$race <- relevel(dt.ndi.ozone.race$race, ref = "A") 
race.A = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(race.A) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")
  out[1,1]<- "A" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:raceB',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:raceH',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:raceW',4]
  race.A <- rbind(race.A, out)
}

save(race.A, 
     file = here('output', 'analysis', 'out-raceA-4.RDa'))

### race Black
dt.ndi.ozone.race$race <- relevel(dt.ndi.ozone.race$race, ref = "B") 
race.B = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(race.B) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")
  out[1,1] <- "B" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:raceA',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:raceH',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:raceW',4]
  race.B <- rbind(race.B, out)
}

save(race.B, 
     file = here('output', 'analysis', 'out-raceB-4.RDa'))

### race Hispanic
dt.ndi.ozone.race$race <- relevel(dt.ndi.ozone.race$race, ref = "H") 
race.H = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(race.H) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")
  out[1,1] <- "H" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:raceA',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:raceB',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:raceW',4]
  race.H <- rbind(race.H, out)
}

save(race.H, 
     file = here('output', 'analysis', 'out-raceH-4.RDa'))

### race White
dt.ndi.ozone.race$race <- relevel(dt.ndi.ozone.race$race, ref = "W") 
race.W = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(race.W) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("race_Cat","Outcome","O3_B","O3_SE","pA","pB","pH","pW")
  out[1,1] <- "W" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:raceA',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:raceB',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:raceH',4]
  race.W <- rbind(race.W, out)
}

save(race.W, 
     file = here('output', 'analysis', 'out-raceW-4.RDa'))

out.race <-na.omit(rbind(race.A, race.B, race.H, race.W))
save(out.race, 
     file = here('output', 'analysis', 'out-race.RDa'))

```


```{r Urbanicity}
dt.ndi.ozone <- dt.ndi.ozone %>% 
  mutate(LocSet = ifelse(LocationSetting == "URBAN AND CENTER CITY", "urban",
                         ifelse(LocationSetting == "SUBURBAN", "suburban", "rural")),
         LocSet = as.factor(LocSet))

### Urban and City Center
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "urban") 
loc.urban = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(loc.urban) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")
  out[1,1]<- "urban" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:LocSetsuburban',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:LocSetrural',4]
  loc.urban <- rbind(loc.urban, out)
}

save(loc.urban, 
     file = here('output', 'analysis', 'out-urban-4.RDa'))


### Suburban
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "suburban") 
loc.suburban = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(loc.suburban) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")
  out[1,1]<- "suburban" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:LocSeturban',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:LocSetrural',4]
  loc.suburban <- rbind(loc.suburban, out)
}

save(loc.suburban, 
     file = here('output', 'analysis', 'out-suburban-4.RDa'))

### Rural
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "rural") 
loc.rural = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(loc.rural) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("Loc_Set","Outcome","O3_B","O3_SE","pU","pS","pR")
  out[1,1]<- "rural" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:LocSeturban',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:LocSetsuburban',4]
  loc.rural <- rbind(loc.rural, out)
}

save(loc.rural, 
     file = here('output', 'analysis', 'out-rural-4.RDa'))

```

```{r Urban SES cat}
dt.ndi.ozone.urban.sescat$sescat<-as.factor(dt.ndi.ozone.urban.sescat$sescat)

### Low SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat, 
                                            ref = "Low") 
ses.Low = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.Low) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "Low" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:sescatMid',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:sescatHigh',4]
  ses.Low <- rbind(ses.Low, out)
}

save(ses.Low, 
     file = here('output', 'analysis', 'out-sesL-4.RDa'))


### Middle SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat, 
                                            ref = "Mid") 
ses.Mid = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.Mid) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "Mid" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sescatLow',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:sescatHigh',4]
  ses.Mid <- rbind(ses.Mid, out)
}

save(ses.Mid, 
     file = here('output', 'analysis', 'out-sesM-4.RDa'))

### High SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat,
                                            ref = "High") 
ses.High = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.High) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "High" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sescatLow',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:sescatMid',4]
  ses.High <- rbind(ses.High, out)
}

save(ses.High, 
     file = here('output', 'analysis', 'out-sesH-4.RDa'))

```

```{r Urban and Suburban SES cat}
dt.ndi.ozone.urbsub.sescat$sescat<-as.factor(dt.ndi.ozone.urbsub.sescat$sescat)

### Low SES
dt.ndi.ozone.urbsub.sescat$sescat <- relevel(dt.ndi.ozone.urbsub.sescat$sescat, 
                                            ref = "Low") 
ses.Low = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.Low) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urbsub.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urbsub.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "Low" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:sescatMid',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:sescatHigh',4]
  ses.Low <- rbind(ses.Low, out)
}

save(ses.Low, 
     file = here('output', 'analysis', 'out-sesL-II-4.RDa'))


### Middle SES
dt.ndi.ozone.urbsub.sescat$sescat <- relevel(dt.ndi.ozone.urbsub.sescat$sescat, 
                                            ref = "Mid") 
ses.Mid = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.Mid) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urbsub.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urbsub.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "Mid" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sescatLow',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:sescatHigh',4]
  ses.Mid <- rbind(ses.Mid, out)
}

save(ses.Mid, 
     file = here('output', 'analysis', 'out-sesM-II-4.RDa'))

### High SES
dt.ndi.ozone.urbsub.sescat$sescat <- relevel(dt.ndi.ozone.urbsub.sescat$sescat,
                                            ref = "High") 
ses.High = matrix(nrow = 1, ncol = 7, byrow = T) 
colnames(ses.High) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urbsub.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urbsub.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 7, byrow = T) 
  colnames(out) <- c("SES_cat","Outcome","O3_B","O3_SE","pL","pM","pH")
  out[1,1]<- "High" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:sescatLow',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:sescatMid',4]
  ses.High <- rbind(ses.High, out)
}

save(ses.High, 
     file = here('output', 'analysis', 'out-sesH-II-4.RDa'))

```

```{r Region}
dt.ndi.ozone <- dt.ndi.ozone %>% 
  mutate(region = ifelse(RegionIV == 1, "W",
                         ifelse(RegionIV == 2, "MW",
                                ifelse(RegionIV == 3, "S", "NE"))),
         region = as.factor(region))

### West
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "W") 
region.W = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(region.W) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")
  out[1,1]<- "W" 
  out[1,2]<- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:regionMW',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:regionS',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:regionNE',4]
  region.W <- rbind(region.W, out)
}

save(region.W, 
     file = here('output', 'analysis', 'out-west-1.RDa'))

### Midwest
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "MW") 
region.MW = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(region.MW) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")
  out[1,1] <- "MW" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:regionW',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:regionS',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:regionNE',4]
  region.MW <- rbind(region.MW, out)
}

save(region.MW, 
     file = here('output', 'analysis', 'out-midwest-1.RDa'))

### South
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "S") 
region.S = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(region.S) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")
  out[1,1] <- "S" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:regionW',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:regionMW',4]
  out[1,8] <- summary(glm_model)$coefficients['O3maxh:regionNE',4]
  region.S <- rbind(region.S, out)
}

save(region.S, 
     file = here('output', 'analysis', 'out-south-1.RDa'))

### Northeast
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "NE") 
region.NE = matrix(nrow = 1, ncol = 8, byrow = T) 
colnames(region.NE) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh*region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 8, byrow = T) 
  colnames(out) <- c("region_Cat","Outcome","O3_B","O3_SE","pW","pMW","pS","pNE")
  out[1,1] <- "NE" 
  out[1,2] <- Y
  # Ozone
  out[1,3] <- coef(glm_model)['O3maxh']
  out[1,4] <- summary(glm_model)$coefficients['O3maxh',2]
  out[1,5] <- summary(glm_model)$coefficients['O3maxh:regionW',4]
  out[1,6] <- summary(glm_model)$coefficients['O3maxh:regionMW',4]
  out[1,7] <- summary(glm_model)$coefficients['O3maxh:regionS',4]
  region.NE <- rbind(region.NE, out)
}

save(region.NE, 
     file = here('output', 'analysis', 'out-northeast-1.RDa'))

#out.race <-na.omit(rbind(race.A, race.B, race.H, race.N, race.W))
#save(out.race, 
#     file = here('output', 'analysis', 'out-race.RDa'))

```

```{r bz12}
out.pm.bz12 = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.bz12) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.bz12[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.bz12, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm.bz12 <- rbind(out.pm.bz12, out) 
}

save(out.pm.bz12, 
     file = here('output', 'analysis', 'out-pm-bz12-1.RDa'))

```

```{r bz24}
out.pm.bz24 = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.bz24) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.bz24[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.bz24, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm.bz24 <- rbind(out.pm.bz24, out) 
}

save(out.pm.bz24, 
     file = here('output', 'analysis', 'out-pm-bz24-1.RDa'))

```

```{r ses - max8h}
out.ses.8h = matrix(nrow = 1, ncol = 3, byrow = T) 
colnames(out.ses.8h) <- c("Outcome", "O3_B", "O3_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3max8h + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 3, byrow = T) 
  colnames(out) <- c("Outcome", "O3_B", "O3_SE")
  out[1,1] <- Y
  out[1,2] <- coef(glm_model)['O3max8h']
  out[1,3] <- summary(glm_model)$coefficients['O3max8h', 2]
  out.ses.8h <- rbind(out.ses.8h, out) 
}
save(out.ses.8h, 
     file = here('output', 'analysis', 'out-ses-8hmax-1.RDa'))

```

```{r ses - avgh}
out.ses.h = matrix(nrow = 1, ncol = 3, byrow = T) 
colnames(out.ses.h) <- c("Outcome", "O3_B", "O3_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3avgh + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 3, byrow = T) 
  colnames(out) <- c("Outcome", "O3_B", "O3_SE")
  out[1,1] <- Y
  out[1,2] <- coef(glm_model)['O3avgh']
  out[1,3] <- summary(glm_model)$coefficients['O3avgh', 2]
  out.ses.h <- rbind(out.ses.h, out) 
}
save(out.ses.h, 
     file = here('output', 'analysis', 'out-ses-avgh-1.RDa'))

```

```{r pm - max8h}
out.pm.8h = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.8h) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3max8h + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3max8h']
  out[1,3] <- summary(glm_model)$coefficients['O3max8h',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm.8h <- rbind(out.pm.8h, out) 
}

save(out.pm.8h, 
     file = here('output', 'analysis', 'out-pm-8hmax-1.RDa'))

```

```{r pm - avgh}
out.pm.h = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.h) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3avgh + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3avgh']
  out[1,3] <- summary(glm_model)$coefficients['O3avgh',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm.h <- rbind(out.pm.h, out) 
}

save(out.pm.h, 
     file = here('output', 'analysis', 'out-pm-avgh-1.RDa'))

```

```{r pm - brfss}
out.pm.brfss = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.brfss) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.brfss[ ,paste0('no_death_', Y, sep = "")] ~ 
                     O3maxh + PM + 
                     X_bmi_Mean + X_raceg_Prop + X_rfsmok_Prop + 
                     X_diabetes_Prop + X_asthma_Prop + X_rfdrhv_Prop +  
                     State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.brfss, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome","O3_B","O3_SE","PM_B","PM_SE")
  out[1,1] <- Y
  # Ozone
  out[1,2] <- coef(glm_model)['O3maxh']
  out[1,3] <- summary(glm_model)$coefficients['O3maxh',2]
  # PM2.5
  out[1,4] <- coef(glm_model)['PM']
  out[1,5] <- summary(glm_model)$coefficients['PM',2] 
  out.pm.brfss <- rbind(out.pm.brfss, out) 
}

save(out.pm.brfss, 
     file = here('output', 'analysis', 'out-pm-brfss-1.RDa'))

```