---
title: "The Impact of Long-Term O3 Exposure on Specific Causes of Death"
substitle: "Does-Response curve and Effect Modification in a US Medicare Cohort"
author: "Fatemeh Kazemi"
date: "6/25/2022"
output: html_document
---

### Variables           - description
    1. SiteID           - unique identifier of each monitor (site)
    2. year             - year
    3. month            - month
    4. age              - age
                          a. in all analysis 
                             65, 66, ..., 90
                          b. in Age effect modification analysis
                             LE75 : less than/equal to 75
                             M75 : More than 75
    5. sex              - sex (F/M)
    6. race             - race 
                          a. in all analysis
                              W  : White
                              NW : Nonwhite
                          b. in Race effect modification analysis
                              A  : Asian
                              B  : Black
                              H  : Hispanic
                              N  : Native American
                              W  : White
    7. StrID            - age-sex-race(asr) strata
    8. no_enrollee      - number of Medicare enrollees of each asr group in each
                          location at the beginning of the month 
    9. no_death_cause   - number of death at each asr group for each cause in 
                          month t for each location
   10. O3maxh           - warm season avg of max daily o3 for each calender year
                          at the given site
   11. O3avgh           - warm season avg of daily avg o3 for each calender year
                          at the given site
   12. O3max8h          - warm season avg of 8h-max daily o3 for each calender year
                          at the given site
   13. PM               - PM2.5 yearly average over the previous year at the 
                          given site up to the given month
   14. ses              - xxx
   15. LocationSetting  - location setting
                          a. URBAN AND CENTER CITY
                          b. SUBURBAN
                          c. RURAL
   16. RegionIV     	  - region as defined in the paper:  1, 2, 3, 4 
                          1 : West
                          2 : Midwest
                          3 : South
                          4 : Northeast
   17. State      	    - state of residence
   18. NO2              - NO2 yearly average over the previous year at the 
                          given site up to the given month
   19. sescat           - SES category for urban or urban/suburban areas

### Models
    1. 
    
###
srun --partition=short  --nodes 1 --ntasks 1 --cpus-per-task 2 --pty --export=ALL --mem=200G --time=24:00:00 /bin/bash
/shared/centos7/r-project/3.6.1/bin/R

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

```{r load packages}
  library(tidyverse)
  library(here)
  library(survival)
  library(stringi)
  library(rms)
  library(pspline)

install.packages('rms')
install.packages('pspline')
```

```{r load data}
load(here('data','analysis','ndi-ozone.RDa'))
load(here('data','analysis','ndi-ozone-age.RDa'))
load(here('data','analysis','ndi-ozone-race.RDa'))
load(here('data','analysis','ndi-ozone-urban-sescat.RDa'))
load(here('data','analysis','ndi-ozone-brfss.RDa'))
```

```{r }
cuz <- c("allcuz",
         "cvd","ihd","chf","cbv",
         "resp","copd","pneu",
         "canc","lungc",
         "seps",
         "VaD","AD","UsD",
         "diabt1","diabt2",
         "kidn")

cuz1 <- c("allcuz","cvd","ihd","chf")

cuz2 <- c("cbv","resp","copd","pneu")

cuz3 <- c("canc","lungc","seps","VaD","AD")

cuz4 <- c("UsD","diabt1","diabt2","kidn")
```

```{r }
cuz <- c("allcuz",
         "cvd","ihd","chf","cbv",
         "resp","copd","pneu",
         "canc","lungc",
         "seps",
         "VaD","AD","UsD",
         "diabt1", "diabt2",
         "kidn")

cuz1 <- c("allcuz","cvd","ihd")
cuz2 <- c("chf","cbv","resp")
cuz3 <- c("copd","pneu")
cuz4 <- c("canc","lungc")
cuz5 <- c("seps","VaD","AD")
cuz6 <- c("UsD","diabt1")
cuz7 <- c("diabt2","kidn")
```

```{r}
#find the knots for 3 - done
dt <- dt.ndi.ozone %>% 
  distinct(SiteID, Year, Month, .keep_all = T)
quantile(dt$O3maxh, c(0.1, 0.5, 0.9))
# 10%        50%        90% 
# 0.04120822 0.05031925 0.05917290 

knotz <- c(0.04120822, 0.05031925, 0.05917290)

knots_3 <- rcspline.eval(dt.ndi.ozone$O3maxh, knots = knotz, inclx = T, norm = 2)
colnames(knots_3) <- c("knot1", "knot2")

knots_3_age <- rcspline.eval(dt.ndi.ozone.age$O3maxh, knots = knotz, inclx = T,
                             norm = 2)
colnames(knots_3_age) <- c("knot1", "knot2")

knots_3_race <- rcspline.eval(dt.ndi.ozone.race$O3maxh, knots = knotz, inclx = T,
                              norm = 2)
colnames(knots_3_race) <- c("knot1", "knot2")

knots_3_sesurb <- rcspline.eval(dt.ndi.ozone.urban.sescat$O3maxh, knots = knotz,
                                inclx = T, norm = 2)
colnames(knots_3_sesurb) <- c("knot1", "knot2")

knots_3_brfss <- rcspline.eval(dt.ndi.ozone.brfss$O3maxh, knots = knotz,
                               inclx = T, norm = 2)
colnames(knots_3_brfss) <- c("knot1", "knot2")

knots_3_8h <- rcspline.eval(dt.ndi.ozone$O3max8h, knots = knotz, inclx = T, 
                            norm = 2)
colnames(knots_3_8h) <- c("knot1", "knot2")

knots_3_avgh <- rcspline.eval(dt.ndi.ozone$O3avgh, knots = knotz, inclx = T, 
                            norm = 2)
colnames(knots_3_avgh) <- c("knot1", "knot2")
```

```{r state + ses + pm}
out.nl.main = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.nl.main) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                           "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~
                     knots_3 + PM + State + ses + strata(StrID),
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")
  out[1,1] <- Y
  # knot1
  out[1,2] <- coef(glm_model)['knot1']
  out[1,3] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,4] <- coef(glm_model)['knot2']
  out[1,5] <- summary(glm_model)$coefficients['knot2',2] 
  out.nl.main <- rbind(out.nl.main, out) 
}

save(out.nl.main, file = here('output', 'analysis', 'out-nl-pm-1.RDa'))
```

```{r state + ses + pm - age}
dt.ndi.ozone.age$age<-as.factor(dt.ndi.ozone.age$age)

### Age LE75
dt.ndi.ozone.age$age <- relevel(dt.ndi.ozone.age$age, ref = "LE75") 
age.nl.le = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(age.nl.le) <- c("Age_Cat", "Outcome", "knot1_B", "knot1_SE",
                         "knot2_B", "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.age[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_age * age + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.age, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("Age_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B",
                     "knot2_SE")
  out[1,1] <- "LE75" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  age.nl.le <- rbind(age.nl.le, out)
}

save(age.nl.le, file = here('output', 'analysis', 'out-le-4.RDa'))

### Age M75
dt.ndi.ozone.age$age <- relevel(dt.ndi.ozone.age$age, ref = "M75") 
age.nl.mt = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(age.nl.mt) <- c("Age_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                         "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.age[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_age * age + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.age, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("Age_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1] <- "M75" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  age.nl.mt <- rbind(age.mt, out)
}

save(age.nl.mt, 
     file = here('output', 'analysis', 'out-mt-1.RDa'))
```

```{r state + ses + pm - sex}
dt.ndi.ozone$sex<-as.factor(dt.ndi.ozone$sex)

### sex Female
dt.ndi.ozone$sex <- relevel(dt.ndi.ozone$sex, ref = "F") 
sex.F = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(sex.F) <- c("sex_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * sex + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("sex_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1] <- "Female" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  sex.F <- rbind(sex.F, out)
}

save(sex.F, file = here('output', 'analysis', 'out-sexF-4.RDa'))

### sex Male
dt.ndi.ozone$sex <- relevel(dt.ndi.ozone$sex, ref = "M") 
sex.M = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(sex.M) <- c("sex_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * sex + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("sex_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1] <- "Male" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  sex.M <- rbind(sex.M, out)
}

save(sex.M, file = here('output', 'analysis', 'out-sexM-4.RDa'))
```

```{r state + ses + pm - race}
### race Asian
dt.ndi.ozone.race <- dt.ndi.ozone.race %>% 
  mutate(race = as.factor(case_when(race != "A" ~ "O",
                          T ~ as.character(race))),
         StrID = stri_replace_all_regex(StrID,
                                  pattern = c('B', 'H', 'W'),
                                  replacement = c('O'), vectorize = F),
         race = relevel(race, ref = "A"))

race.A = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(race.A) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                      "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3_race * race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "Asian" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  race.A <- rbind(race.A, out)
}

save(race.A, file = here('output', 'analysis', 'out-raceA-1.RDa'))

### race Black
dt.ndi.ozone.race <- dt.ndi.ozone.race %>% 
  mutate(race = as.factor(case_when(race != "B" ~ "O",
                          T ~ as.character(race))),
         StrID = stri_replace_all_regex(StrID,
                                  pattern = c('A', 'H', 'W'),
                                  replacement = c('O'), vectorize = F),
         race = relevel(race, ref = "B"))

race.B = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(race.B) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                      "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3_race * race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "Black" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  race.B <- rbind(race.B, out)
}

save(race.B, file = here('output', 'analysis', 'out-raceB-1.RDa'))

### race Hispanic
dt.ndi.ozone.race <- dt.ndi.ozone.race %>% 
  mutate(race = as.factor(case_when(race != "H" ~ "O",
                          T ~ as.character(race))),
         StrID = stri_replace_all_regex(StrID,
                                  pattern = c('A', 'B', 'W'),
                                  replacement = c('O'), vectorize = F),
         race = relevel(race, ref = "H"))

race.H = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(race.H) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                      "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_race * race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "Hispanic" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  race.H <- rbind(race.H, out)
}

save(race.H, file = here('output', 'analysis', 'out-raceH-1.RDa'))

### race White
dt.ndi.ozone.race <- dt.ndi.ozone.race %>% 
  mutate(race = as.factor(case_when(race != "W" ~ "O",
                          T ~ as.character(race))),
         StrID = stri_replace_all_regex(StrID,
                                  pattern = c('A', 'B', 'H'),
                                  replacement = c('O'), vectorize = F),
         race = relevel(race, ref = "W"))

race.W = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(race.W) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                      "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.race[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_race * race + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.race, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("race_Cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "White" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  race.W <- rbind(race.W, out)
}

save(race.W, file = here('output', 'analysis', 'out-raceW-1.RDa'))
```

```{r state + ses + pm - urbanicity}
dt.ndi.ozone <- dt.ndi.ozone %>% 
  mutate(LocSet = ifelse(LocationSetting == "URBAN AND CENTER CITY", "urban",
                         ifelse(LocationSetting == "SUBURBAN", "suburban", 
                                "rural")),
         LocSet = as.factor(LocSet))

### Urban and City Center
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "urban") 
loc.urban = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(loc.urban) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                         "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "urban" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  loc.urban <- rbind(loc.urban, out)
}

save(loc.urban, file = here('output', 'analysis', 'out-urban-4.RDa'))

### Suburban
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "suburban") 
loc.suburban = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(loc.suburban) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE",
                            "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "suburban" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  loc.suburban <- rbind(loc.suburban, out)
}

save(loc.suburban, file = here('output', 'analysis', 'out-suburban-4.RDa'))

### Rural
dt.ndi.ozone$LocSet <- relevel(dt.ndi.ozone$LocSet, ref = "rural") 
loc.rural = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(loc.rural) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                         "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * LocSet + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("Loc_set", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "rural" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  loc.rural <- rbind(loc.rural, out)
}

save(loc.rural, file = here('output', 'analysis', 'out-rural-4.RDa'))
```

```{r state + ses + pm - urban SES cat}
dt.ndi.ozone.urban.sescat$sescat<-as.factor(dt.ndi.ozone.urban.sescat$sescat)

### Low SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat, 
                                            ref = "Low") 
ses.Low = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(ses.Low) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                       "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_sesurb * sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "Low" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  ses.Low <- rbind(ses.Low, out)
}

save(ses.Low, file = here('output', 'analysis', 'out-sesL-4.RDa'))

### Middle SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat, 
                                            ref = "Mid") 
ses.Mid = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(ses.Mid) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                       "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3_sesurb * sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "Mid" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  ses.Mid <- rbind(ses.Mid, out)
}

save(ses.Mid, file = here('output', 'analysis', 'out-sesM-4.RDa'))

### High SES
dt.ndi.ozone.urban.sescat$sescat <- relevel(dt.ndi.ozone.urban.sescat$sescat,
                                            ref = "High") 
ses.High = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(ses.High) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                        "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.urban.sescat[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3_sesurb * sescat + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.urban.sescat, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("SES_cat", "Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                     "knot2_SE")
  out[1,1]<- "High" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  ses.High <- rbind(ses.High, out)
}

save(ses.High, file = here('output', 'analysis', 'out-sesH-4.RDa'))
```

```{r state + ses + pm - region}
dt.ndi.ozone <- dt.ndi.ozone %>% 
  mutate(region = ifelse(RegionIV == 1, "W",
                         ifelse(RegionIV == 2, "MW",
                                ifelse(RegionIV == 3, "S", "NE"))),
         region = as.factor(region))

### West
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "W") 
region.W = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(region.W) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE", 
                        "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3 * region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                     "knot2_B", "knot2_SE")
  out[1,1]<- "W" 
  out[1,2]<- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  region.W <- rbind(region.W, out)
}

save(region.W, file = here('output', 'analysis', 'out-west-4.RDa'))

### Midwest
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "MW") 
region.MW = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(region.MW) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE", 
                         "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3 * region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                     "knot2_B", "knot2_SE")
  out[1,1] <- "MW" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  region.MW <- rbind(region.MW, out)
}

save(region.MW, file = here('output', 'analysis', 'out-midwest-4.RDa'))

### South
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "S") 
region.S = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(region.S) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                        "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3 * region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                     "knot2_B", "knot2_SE")
  out[1,1] <- "S" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  region.S <- rbind(region.S, out)
}

save(region.S, file = here('output', 'analysis', 'out-south-4.RDa'))

### Northeast
dt.ndi.ozone$region <- relevel(dt.ndi.ozone$region, ref = "NE") 
region.NE = matrix(nrow = 1, ncol = 6, byrow = T) 
colnames(region.NE) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                         "knot2_B", "knot1_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                    knots_3 * region + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 6, byrow = T) 
  colnames(out) <- c("region_cat", "Outcome", "knot1_B", "knot1_SE",
                     "knot2_B", "knot2_SE")
  out[1,1] <- "NE" 
  out[1,2] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  region.NE <- rbind(region.NE, out)
}

save(region.NE, file = here('output', 'analysis', 'out-northeast-4.RDa'))
```


```{r state + ses + pm - max8h}
colnames(knots_3) <- c("knot1", "knot2")
out.pm.8h = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.8h) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_8h + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")
  out[1,1] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  out.pm.8h <- rbind(out.pm.8h, out) 
}

save(out.pm.8h, file = here('output', 'analysis', 'out-pm-8hmax-4.RDa'))
```

```{r state + ses + pm - avgh}
out.pm.h = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.h) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_avgh + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")
  out[1,1] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  out.pm.h <- rbind(out.pm.h, out) 
}

save(out.pm.h, file = here('output', 'analysis', 'out-pm-avgh-4.RDa'))
```

```{r pm - brfss0}
out.pm.brfss0 = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.brfss0) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", 
                             "knot2_SE")

for (Y in cuz4){
  glm_model <- glm(dt.ndi.ozone.brfss[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_brfss + PM + State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.brfss, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")
  out[1,1] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2]
  out.pm.brfss0 <- rbind(out.pm.brfss0, out) 
}

save(out.pm.brfss0, file = here('output', 'analysis', 'out-pm-brfss0-4.RDa'))
```

```{r pm - brfss}
out.pm.brfss = matrix(nrow = 1, ncol = 5, byrow = T) 
colnames(out.pm.brfss) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B",
                            "knot2_SE")

for (Y in cuz1){
  glm_model <- glm(dt.ndi.ozone.brfss[ ,paste0('no_death_', Y, sep = "")] ~ 
                     knots_3_brfss + PM + 
                     X_bmi_Mean + X_raceg_Prop + X_rfsmok_Prop + 
                     X_diabetes_Prop + X_asthma_Prop + X_rfdrhv_Prop +  
                     State + ses + strata(StrID), 
                   offset = (log(no_enrollee)), 
                   data = dt.ndi.ozone.brfss, family = poisson(link = "log"))
  out = matrix(nrow = 1, ncol = 5, byrow = T) 
  colnames(out) <- c("Outcome", "knot1_B", "knot1_SE", "knot2_B", "knot2_SE")
  out[1,1] <- Y
  # knot1
  out[1,3] <- coef(glm_model)['knot1']
  out[1,4] <- summary(glm_model)$coefficients['knot1',2]
  # knot2
  out[1,5] <- coef(glm_model)['knot2']
  out[1,6] <- summary(glm_model)$coefficients['knot2',2] 
  out.pm.brfss <- rbind(out.pm.brfss, out) 
}

save(out.pm.brfss, file = here('output', 'analysis', 'out-pm-brfss-1.RDa'))
```

